Vulnerability Analysis of Container Images in Neuroimaging

### 2020-06-30 paper.tex
Comments and edits in section II

@@

Since the aim of this reseach work is to detect security vulnerabilities
in container images and attempt to examine the effect of different
manipulation of these images, it is needed to have sufficient number of
images. Additionally, for the purpose of detecting vulnerabilities,
utilization of image scanners is required. We utilize container
images from two different containerization frameworks as well as
various image scanners tools.

%This study involves several image scanning experiments. To begin with,
%we scan the images as is to report the vulnerabilities
%inside the images. Updating and shrinking the size of these images is likely to play a role in vulnerabilities. Therefore, we
%update the images and then rescan all these
%images.
%Subsequently, we shrink the size of the images
%meaning that remove unnecessary packages from the images to see the effect on the number of
%vulnerabilities in the images.
%Lastly, we update and shrink the image size together and then
%rescan for the vulnerabilities.
%
%In this section, we provide
%insight
%into the container images and the image scanners that we used in our study.
%The image scanners refer to different Linux
%distributions/releases, which have different vulnerability data and is likely to
%create discrepancies in results. Therefore, in the last, this section presents a
%description of these varying Linux distributions/releases and their
%vulnerability databases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%As we are taking a particular use case of containers from
%neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
%in this section we summarize the data and tools 
%that are used in CONP. CONP is a national platform for sharing neuroscience
%research data and aims at creating an interactive interface for neuroscientists and
%clinical neuroscience. The main goal of the CONP platform is to store, process, and
%distribute massive amounts of data produced by modern neuroscience.
%Here, we summarize all the resources that are
%used by CONP to function.

%\subsection{Container Tools}
%
%
%In this paper, we consider two popular container tools i.e Docker and Singularity because
%neuroimaging uses images from these two tools.
%Container tools are capable of packing and running an application in an isolated environment that has
%the application's dependencies,
%required libraries, and configuration files for the
%application to function properly.

%\subsubsection{Docker}

%Docker uses a client-server architecture, where client, containers, communicate to
%the server, Docker Daemon, which is also known as the Docker engine.
%Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.

%consists of the following three main components: 
%
%\textit{Docker Daemon:} It acts as a server. It is
%a long-running process that manages all Docker images, containers, storage volumes, and networks.
%
%\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
%to talk to the \textit{Docker Daemon}.
%
%\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
%Docker runs a software, \textit{Docker daemon}, on the host machine.

%Docker Engine, which runs as root, is remotely controlled through a
%UNIX socket. It is responsible for launching and managing containers,
%consequently, when a container runs, the container is spawned as a
%child process of this root-owned daemon.
%
%\begin{comment}
%It is responsible for launching containers, their
%isolation, and spawning shells into the containers. It is also
%responsible for managing Docker images i.e \textit{pull} and \textit{push}
%from image repository, building images from Dockerfiles, signing them, etc.
%When a Docker container runs, the container process is spawned as a
%child of this root owned daemon. 
%\end{comment}
%As Docker users directly interact with the
%Docker daemon through Command Line Interface (CLI) i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
%If a user gets root privileges, it
%introduces unthinkable security risks for multi-tenant shared
%environments. Due to this reason, Docker is not supported by
%HPC environments.
%
%Docker images are organized as a series of layers stacked on top of each
%other and identified by unique layer identifiers. If a layer is reused
%in different images it will
%have the same id across images. Each layer consists of a filesystem diff
%with respect to the layer below.
%
%\subsubsection{Singularity}
%
%As Docker is not suitable for HPC systems, therefore, Singularity came up with a new approach
%of packing and running applications in containers. 
%In contrast to Docker,
%Singularity does not run containers as root. Consequently, users cannot escalate
%privileges in Singularity containers making it suitable for HPC environments.
%
%A Singularity image is a single immutable file and
%does not contain layers.
%Once a Singularity image is created, it cannot be changed, consequently,
%it can be used for reproducing the results of scientific
%experiments.

%\begin{comment}
%Singularity offers mobility of compute by facilitating portable environments 
%through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
%is created, it is hashed using SHA-256. Hence, it cannot be changed
%once it is created, consequently, it can be used for reproducing the results of
%scientific experiments. Main features provided by
%Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
%We used Singularity version $2.5.2$ in our experiments.
%Users can easily access files, devices, sockets, ports of the host system from
%the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
%into the running container. Additional directories can be specified with \textit{--bind}
%to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
%However namespaces can be requested if required. Users cannot escalate privileges inside
%Singularty containers. This is because Singularity do not run containers as root.
%Instead, a user inside Singularity container is the same user outside the container.
%
%\subsection{Container Image Formats}
%
%A container image is a package that contains an application along with its
%required dependencies and libraries.
%Both, Docker and Singularity, have different image formats. Below we provide a description of both image
%formats.
%
%\subsubsection{Docker Image Format}
%
%Docker images are organized as a series of layers stacked on top of each
%other and identified by unique layer identifiers. If a layer is reused
%in different images it will
%have the same id across images. Each layer consists of a filesystem diff
%with respect to the layer below. 
%DockerHub uses gzip compression for
%transferring layers.There are two ways to create a Docker image. The
%first is to use an existing Docker image as a base image and then build a
%new image from that one, by making changes in the filesystem, which is
%saved as a new layer of the Docker image. The second way is to build a new
%Docker image from scratch.Docker supports several different storage drivers.
%\textit{Overlay2} is the preferred storage driver used by Docker for all currently
%supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
%older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
%Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
%zfs, and vfs}
%
%\subsubsection{Singularity Image Format}
%
%On the other hand, a Singularity image is a single immutable file and 
%does not contain layers.
%Once a Singularity image is created, it cannot be changed, consequently,
%it can be used for reproducing the results of scientific
%experiments.
%Singularity takes snapshot, locks, and archives the developed application,
%which is known as Singularity image.
%It means that Singularity image is a single immutable file that can be moved around as
%any other file. This file can be checksummed, signed, and easily
%used for verification purposes. Singularity containers use Squashfs file format
%by default. It is read-only file system in Linux, which uses compression for files,
%inodes, and directories. However, Singularity also supports two other 
%formats i.e \textit{sandbox} format
%(which is just a chroot
%directory) and \textit{writable} format (the ext3 file system).
%While publishing experimental results, authors can also publish Singularity
%image along with its hash, which allow other researchers to verify results.
%\end{comment}
\subsection{Container Images}

We scan a total of 44 container images taken from two containerization frameworks
used in neuroscience: BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
Out of these 44 images, 26 were obtained from BIDS apps
\href{https://bids-apps.neuroimaging.io/apps/}{(https://bids-apps.neuroimaging.io/apps/)} 
and 18 from Boutiques. In fact, at the time of the study, BIDS apps has 27 images,
out of which one wasn't available on DockerHub. Boutiques has 49 images, listed using
Boutiques \texttt{bosh search} command,
however, only 23 unique were listed, out of which 3 couldn't be retrieved and 2
we decided to ignore as they were already included in BIDS apps. All the final 26 images
from BIDS apps are Docker images, whereas Boutiques contain 18 Docker images
and 6 Singularity images.

%Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
%{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
%the study, we studied 26
%unique Docker images as one wasn't available on DockerHub. Among the 49
%Boutiques applications available at the time of the study, listed using
%Boutiques \texttt{bosh search} command, 23 unique container images were
%listed including 3 that couldn't be retrieved and 2 that were already
%included in BIDS apps. The resulting 18 images included 12 Docker images
%and 6 Singularity images.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

%\begin{comment}
%\subsubsection{ReproNim}
%
%ReproNim is a Center for Reproducible Neuroimaging Computation. It is a vision
%to help neuroscientists in reproducing neuroimaging research. Repronim
%uses RepronIn, BrainVerse, Neuroimaging Computation Environments Manager (NICEMAN),
%and NeuroBlast software tools for its
%functioning. ReproIn is a software that automate acquisition and conversion
%of collected MRI data to BIDS standard format with DataLad version management~\cite{kennedy2019everything}.
%BrainVerse is a cross-platform software framework and collaborative desktop application
%that helps in managing, tracking, and sharing information.
%NICEMAN is a software system that tracks and manages available computation resources
%and makes their use in a scalable and reproducible way.
%Neuroblast is a service that facilitates data sharing of existing studies, and it also
%helps users to search similar studies based on combination of analysis,
%tasks and activation patterns. There are currently 28 different Singularity
%images used by Repronim. 
%
%\subsection{Other images}
%
%\TG{We could also use selected images from DockerHub or SingularityHub. For
%instances the ones used by AFNI or other neuroimaging tools not represented
%in Boutiques or BIDS Apps. However we wouldn't be able to shrink these
%images unless we identified specific command-lines to run.}
%
%\end{comment}

@@

%Container image scanners can be broadly categorized into static and dynamic
%scanners. Static scanning performs analysis on a image without running it
%as a container.

%Therefore, package manager, which is a executable file,
%cannot be used to extract required data while statically extracting image data.
%Thus, scanners parse different files for extracting image data e.g, installed packages, their versions,
%and OS distribution etc. For instance, in Debian and Ubuntu, \textit{/var/lib/dpkg/status} file
%can be parsed to get a list of installed packages and in the same way \textit{/etc/os-release} file can be
%parsed to get information about OS distribution.
%Whereas in dynamic scanning, a container is deployed from the image first and then
%package manager of the image is executed inside the container to collect required data.

%\subsubsection{Scanning tools used}

%\begin{comment}
%Out of the various container image scanning tools available to scan Docker images,
%we selected Anchore~\cite{github_2019}
%and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
%we use Stools, which is specially designed for Singularity images. This tool internally uses
%Clair Scanner tool so we included ClairScanner also in our experiements to compare
%performance of both the tools. So total there are three scanners for Docker images
%and one scanner for Singularity images.
%\end{comment}

@@

%Vuls support both static as well as dynamic
%scanning till version 0.9.5, however, in our experiments we used it dynamically.
%On the contrary, the others
%are static scanners.

@@

Anchore is an end-to-end, open-source container security platform. It
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
%\begin{comment}
%Anchore is a set of tools, which users can
%employ for scanning container images and applying custom policies to them.
%It provides visibility and transparency of the container environment.
%\end{comment}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
%\begin{comment}
%Anchore offers services in two ways: Anchore Engine and Anchore
%Command Line Interface (CLI). Anchore Engine is available as a Docker
%image, which is available on Docker Hub. Anchore Engine CLI provides
%command line interface in addition to Anchore Engine REST API. 
%\end{comment}
It can be
installed directly on the host and used to inspect images.
In our experiments, we use a Docker image in order to have access to Anchore Engine version 0.5.0 with the 
Anchore vulnerability database version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources, for instance, Ubuntu launchpad database to get
vulnerability data related to Ubuntu.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
It offers both static and dynamic scanning. In our experiments, we use
it to dynamically scan containers.
Using a dynamic scanning technique, it offers
remote and local scans at the time of writing. The remote scan sets up only one machine to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. 
%Further, Vuls offer a fast scan, fast root scan,
%and deep scan mode.
%The Fast scan is performed without root privileges, whereas a fast root scan is
%performed with root privileges. The latter also uses checkrestart utility to 
%detect processes that are updated but not yet restarted because if they are not
%restarted, updates are not effective. Fast root scan also detects these
%processes. Both fast scan and fast root scan are performed offline without Internet
%access, and put almost no load on the scan target server. The Deep scan uses
%root privileges for scanning and is used to get a more detailed scan. It checks
%changelogs, which puts more load on the target server.

In our experiments, we use a Vuls Docker image having version 0.9.0. %with fast scan mode.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
It is worth noting that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are hard to scan with Vuls.

@@

Clair-scanner is a static vulnerability scanner for Docker containers.
%CoreOS originally created Clair, a static vulnerability scanner for containers. 
%The main goal of the
%tool is to provide a transparent look of container’s security. Clair scans container images in regular
%intervals, and stores metadata of vulnerabilities, after getting from configured
%set of sources. 
%Clair API can be used by clients to query its database to get
%the list of vulnerabilities that a particular image has. Clair sends a notification
%to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
%is a registry to store images privately, uses Clair internally as the security engine. 
%However, Clair does not 
%provide the facility for comparing
%the vulnerability list of a particular image against a whitelist of vulnerabilities that you
%want to ignore~\cite{arminc_2019}. 
%So, to remove
%that drawback, another tool, Clair Scanner can be used. 
It scans the image, prepares the list of
vulnerabilities, compares that list against a whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair-scanner utilizes the Ubuntu CVE tracker to obtain  Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updates its database, this image is also updated with the required information.

In our experiments, we use a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
last updated on 2019-09-18. We perform
scanning on 2019-09-25.

@@

Continuous Integration (CI) allows smaller code changes, fault isolations,
faster release date, etc. Two types of CI are commonly used : TravisCI and
CircleCI. The former targets open source projects that need to be tested in
different environments, whereas the latter targets smaller projects where
integration needs to be done as fast as possible. Stools uses CoreOS's Clair, which
is used for Docker images, in combination with CI to allow scanning of
Singularity images.
%Stools combines CoreOS's Clair with Continuous Integration (CI)
%for scanning Singularity images for vulnerabilities.
%Initially, Clair was intended to scan Docker images only. This tool does not fit well
%to scan Singularity images because of the different image formats.
%However, TravisCI and CircleCI are commonly used for testing code, and these
%services also offer running containers. Stools combined both these concepts.
It involves spinning a Clair container during testing and building a
Singularity image, and scanning it before the image is finalized.

@@

%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c},
%        table head =Singularity Images & {Vulnerabilities by Stools}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{Singularityresults.csv}{}{\csvlinetotablerow}%
%       \centering
%        \caption{\label{sing}Number of Vulnerabilities in Singularity images}
%\end{table}

%\begin{table*}
%  \caption{some table}
%	\begin{tabular}{>|{\bfseries}c| c| c| *{4}{c|}}\hline
%	  \multirow{2}{*}{\bfseries Image Labels} & 
%	  \multirow{2}{*}{\bfseries Image Names} & 
%	  \multirow{2}{*}{\bfseries OS} & 
%	  \multicolumn{4}{c|}{\bfseries Vulnerabilities} \\\cline{2-5} 
%                       & \textbf{A} & \textbf{C} & \textbf{V}  & \textbf{S} \\ \hline
%a	& bids/example	& ubuntu:14.04	& 838	& 663	& 683	& \\ \hline
%b	& bids/freesurfer	& ubuntu:14.04	& 353	& 215	& 192	& \\ \hline
%c	& bids/ndmg	& ubuntu:14.04	& 934	& 757	& 782	& \\ \hline
%d	& bids/broccoli:v1.0.0	& centos 6	& 79	& 79	& 117	& \\ \hline
%e	& bids/fibredensityandcrosssection	& ubuntu:14.04	& 1086	& 849	& 868	& \\ \hline
%f	& bids/spm	& ubuntu:14.04	& 191	& 246	& 235	& \\ \hline
%g	& poldracklab/mriqc:0.15.0	& ubuntu:16.04	& 432	& 328	& 332	& \\ \hline
%h	& bids/cpac:v1.0.1a\_22	& ubuntu:16.04	& 698	& 524	& 535	& \\ \hline
%I	& bids/hyperalignment	& ubuntu:16.04	& 1717	& 1327	& 1433	& \\ \hline
%j	& bids/mindboggle:0.0.4-1	& debian:8	& 671	& 955	& 569	& \\ \hline
%k	& bids/mrtrix3\_connectome	& ubuntu:18.04	& 275	& 157	& 158	& \\ \hline
%l	& bids/rs\_signal\_extract:0.1	& ubuntu:16.04	& 867	& 454	& 473	& \\ \hline
%m	& bids/aa:v0.2.0	& ubuntu:14.04	& 189	& 244	& 233	& \\ \hline
%n	& bids/niak	& ubuntu:16.04	& 1482	& 1366	& 1420	& \\ \hline
%o	& bids/oppni:v0.7.0-1	& ubuntu:14.04	& 913	& 698	& 723	& \\ \hline
%p	& poldracklab/fmriprep:unstable	& ubuntu:16.04	& 516	& 355	& 393	& \\ \hline
%q	& bids/brainiak-srm	& ubuntu:16.04	& 897	& 484	& 503	& \\ \hline
%r	& bids/nipypelines:0.3.0	& debian:8	& 641	& 878	& 451	& \\ \hline
%s	& bids/hcppipelines:v3.17.0-18	& debian:8	& 526	& 873	& 620	& \\ \hline
%t	& bids/magetbrain	& ubuntu:18.04	& 112	& 117	& 126	& \\ \hline
%u	& bids/tracula:v6.0.0-4	& ubuntu:14.04	& 874	& 664	& 683	& \\ \hline
%v	& bids/baracus	& ubuntu:14.04	& 172	& 238	& 216	& \\ \hline
%w	& bids/antscorticalthickness:v2.2.0-1	& ubuntu:17.04	& 289	& 27	& no oval data	& \\ \hline 
%x	& bids/dparsf:v4.3.12	& ubuntu:14.04	& 507	& 750	& 757	& \\ \hline
%y	& bids/afni\_proc	& ubuntu:17.10	& 67	& 16	& no oval data	& \\ \hline
%z	& bids/rshrf:1.0.1	& alpine:3.8.4	& 5	& 3	& 3	& \\ \hline
%aa	& bids/ndmg:v0.1.0	& ubuntu 14.04	& 934	& 758	& 782	& \\ \hline
%ab	& mcin/qeeg:latest	& centos 7	& 46	& 46	& 142	& \\ \hline
%ac	& camarasu/creaphase:0.3	& centos 7	& 54	& 54	& 186	& \\ \hline
%ad	& bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest	& centos 7	& 70	& 76	& 157	& \\ \hline
%ae	& mcin/docker-fsl:latest	& centos 7	& 75	& 75	& 201	& \\ \hline
%af	& gkiar/onevoxel:v0.3.0rc2	& alpine 3.7.1	& 5	& 2	& 2	& \\ \hline
%ag	& bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest	& centos 7	& 70	& 76	& 157	& \\ \hline 
%ah	& bt5e/ants:latest	& centos 7	& 150	& 156	& 336	& \\ \hline
%ai	& poldracklab/fmriprep:1.2.3	& ubuntu 16.04	& 591	& 441	& 447	& \\ \hline
%aj	& gkiar/dwipreproc\_fsl-5.0.11\_minified	& ubuntu 16.04	& 391	& 258	& 263	& \\ \hline
%ak	& gkiar/mask2boundary:v0.1.0	& alpine 3.9.0	& 15	& 11	& 11	& \\ \hline
%al	& mcin/ica-aroma:latest	& centos 7	& 75	& 75	& 202	& \\ \hline
%am	& c3genomics/genpipes	& 	& 	& 	& 	& 99 \\ \hline
%an	& bioinformatics-group/aqua-singularity-recipe	& 	& 	& 	& 	& 7 \\ \hline
%ao	& MontrealSergiy/BEst	& 	& 	& 	& 	& 106 \\ \hline
%ap	& shub://aces/cbrain-containers-recipes:fsl\_v6.0.1	& 	& 	& 	& 	& 206 \\ \hline
%aq	& shots47s/bids-freesurfer-6.0	& 	& 	& 	& 	& 212 \\ \hline
%ar	& shots47s/bids-fmriprep-1.2.3	& 	& 	& 	& 	& 453 \\ \hline
%  \end{tabular}
%  \end{table*}

@@

Through our experiments, we find that image scanners report vulnerabilities 
differently depending on the different Linux release types. So, it is 
important to provide an overview of these Linux releases types. 
BIDS app and Boutiques images in our experiments have diverse Linux
distributions, such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution has different releases in general. To illustrate, we here examine Ubuntu as an example,
since it is heavily utilised in our experiments. However, other distributions also have
similar release trend. Ubuntu releases
can be of two types: Regular or Long Term Support (LTS).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

>>>>

\todo{Add related work on vulnerability scanning}

@@

Since the aim of this research work is to detect security vulnerabilities
in container images and attempt to examine the effect of different
manipulation of these images, it is needed to have a representative set
images. Additionally, for the purpose of detecting vulnerabilities,
utilization of image scanners is required. We utilize container
images from two popular application frameworks, as well as
four of the main image scanners.

\subsection{Container Images}

We scan a total of 44 container images taken from two containerization frameworks
used in neuroscience: BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}.
Out of these 44 images, 26 were obtained from BIDS apps
\href{https://bids-apps.neuroimaging.io/apps/}{(https://bids-apps.neuroimaging.io/apps/)} 
and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
out of which one wasn't available on DockerHub. Boutiques had 49 images, listed using
Boutiques \texttt{bosh search} command,
however, only 23 unique images were listed, out of which 3 couldn't be retrieved and 2
 were already included in BIDS apps. All the final 26 images
from BIDS apps are Docker images, whereas Boutiques contains 18 Docker images
and 6 Singularity images.

@@

@@

@@

Anchore is an end-to-end, open-source container security platform. It
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
It can be
installed directly on the host and used to inspect images.
In our experiments, we use Anchore Engine version 0.5.0 through Docker image \todo{insert name}, and
Anchore vulnerability database version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources, for instance, Ubuntu launchpad database to get
vulnerability data related to Ubuntu.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
starts a container for every image to test, and queries the package manager in the image through SSH.
We use Vuls 0.9.0, executed through Docker image \todo{add Docker image name}. Vuls gets data from the Open Vulnerability and Assessment Language (OVAL) database.
It is worth noting that there is no OVAL data for Ubuntu 17.04 and 17.10 distributions,
meaning that images with these distributions cannot be scanned with Vuls.

@@

Clair-scanner is a static vulnerability scanner for Docker containers.
It scans the image, prepares the list of
vulnerabilities, compares that list against a whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair-scanner utilizes the Ubuntu CVE tracker to obtain  Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updates its database, this image is also updated with the required information.
We use Clair-scanner version 2.0.6, executed through  Docker image arminc/clair-local-scan:v2.0.6. 
We use another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
last updated on 2019-09-18.

@@

\todo{remove mentioning of CI, rewrite this paragraph.}
Continuous Integration (CI) allows smaller code changes, fault isolations,
faster release date, etc. Two types of CI are commonly used : TravisCI and
CircleCI. The former targets open source projects that need to be tested in
different environments, whereas the latter targets smaller projects where
integration needs to be done as fast as possible.

Stools uses CoreOS's Clair, which
is used for Docker images, in combination with CI to allow scanning of
Singularity images.
It involves spinning a Clair container during testing and building a
Singularity image, and scanning it before the image is finalized.

@@

@@

Through our experiments, we find that image scanners report vulnerabilities 
differently depending on the different Linux release types. So, it is 
important to provide an overview of these Linux releases types. 
BIDS app and Boutiques images in our experiments have diverse Linux
distributions, such as Ubuntu, CentOS, Debian, and Alpine. Further, a particular
distribution has different releases in general. To illustrate, we here examine Ubuntu as an example,
since it is heavily utilized in our experiments. 
\todo{Explain the situation with centos, update figure 3 accordingly.}
However, other distributions also have
similar release trend. Ubuntu releases
can be of two types: Regular or Long Term Support (LTS).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.
